Choosing climate forcing for numerical simulations of the Cordilleran ice sheet

### 2013-02-21 sections/results.tex
Uneasy area calculation becomes arbitrary choice

For each climate forcing, we selected the simulation that lead to a glaciated area closest to geomorphological reconstruction. This was done using the LGM extent countour from \needref shown in Figure~\ref{fig:locmap}, which covers an area of XXX \todo{Compute geomorpho-based ice cover area}. These ``best'' runs are presented in Figure~\ref{fig:best} along with the associated temperature offset values. We observe that although similar in size, the selected ice sheets are different in shape and flow patterns. More particularly, NCEP/NCAR, CFSR and ERA-Interim ice sheets cover large territories in Yukon and Alaska that where shown to have remained ice-free for at least several glacial cycles.\needref

>>>>

To compare modelled ice sheets of similar size, we selected for each climate forcing the simulation that lead to a glaciated area closest to an arbitrary target of $4\,\times10^6\,\unit{km^2}$. These qualitative ``best'' runs are presented in Figure~\ref{fig:best} along the associated temperature offset values. We observe that although similar in size, the selected ice sheets are different in shape and flow patterns. More specifically, NCEP/NCAR, CFSR and ERA-Interim ice sheets cover large territories in Yukon and Alaska that where shown to have remained ice-free for at least several glacial cycles.\needref
